# Here is where the show begins

In this file we'll analyze the 'aggregated_data.csv' file containing data about all
selected airbnb listings to choose which one is the best choice for our client

```{r load all packages and the csv file}
library(dplyr)
library(tidyvese)
library(tidyr)

setwd("/home/igorregly/google-data-analytics-capstone-project/")
all_data <- read.csv('./aggregated_data.csv', sep=',')

# View(all_data)
```

To choose the best listing for our client we'll create a score using the variable available on the data frame to weigh accordingly the preferences of the client.
After interviewing our client we get these information about their priorities:
1. privacy
2. price
3. location

Besides, they are 4 people and anyone doesn't drive. So, the distance to a means of public transport is an important point.
4. distance to public transport

First, we have to normalize all variables that will be used to build the score.

To do that we'll use the Min-Max Normalization method to transform all values on a value between 0 and 1
```{r normalize the variables}
min_max_normalization <- function(s) {
    min_v <- min(s)
    max_v <- max(s)

    serie <- sapply(s, function(x) (x - min_v) / (max_v - min_v))

    return(serie)
}

# create normalized columns
norm_df <- transform(all_data,
                    norm_realSum = min_max_normalization(realSum),
                    norm_cleanRating = min_max_normalization(cleanliness_rating),
                    norm_csat = min_max_normalization(guest_satisfaction_overall),
                    norm_centerDist = min_max_normalization(dist),
                    norm_metroDist = min_max_normalization(metro_dist))

# covnert the booleans columns to numerics ones
bool_cols <- c('room_shared', 'room_private', 'host_is_superhost')

norm_df[bool_cols] <- apply(norm_df[bool_cols], 2, function(x) as.numeric(as.logical(x)))


# View(norm_df)
```

After created the norm columns, we'll select the ones that will be used to create the score
```{r selecting columns to use}
to_selec_cols <- c("realSum",
                    "room_type",
                    "room_shared",
                    "bedrooms",
                    "person_capacity",
                    "lng",
                    "lat",
                    "city",
                    "type",
                    "norm_realSum",
                    "norm_cleanRating",
                    "norm_csat",
                    "norm_centerDist",
                    "norm_metroDist")

selec_cols_df <- norm_df %>% select(all_of(to_selec_cols))
# View(selec_cols_df)
```

With all set, we can now create the score to help us to choose the better list to our client.
To do that, we will create a vector with weight values accordingly the clients priorities viewed before, and then multiply the columns with these vectors.

1. privacy
2. price & location
3. location

```{r}
weight_values <- c(0.9, 0.7, 0.5)

weighted_df <- selec_cols_df %>%
    mutate(
        weighted_realSum = norm_realSum * weight_values[2],
        weighted_centerDist = norm_centerDist * weight_values[2],
        weighted_metroDist = norm_metroDist * weight_values[2],
        weighted_cleanRating = norm_cleanRating * weight_values[3],
        weighted_csat = norm_csat * weight_values[3],
        score = -(weighted_realSum) + weighted_cleanRating + weighted_csat + -(weighted_centerDist) + -(weighted_metroDist)
    )

# View(weighted_df)
```

Because the privacy is very important to our client, before to create the charts we'll filter out only the listings that are private rooms and, obviously, because they are 4,
we'll also filter out only the listings that have 4 bedrooms.

In the same chunk code we'll select the columns that will be used to create our map.

```{r filter the private listings and select columns}
only_private_rooms <- weighted_df[weighted_df$room_shared == 0 & weighted_df$person_capacity >= 4, ]

cols = c(
    'realSum',
    'room_type',
    'score',
    'lat',
    'lng',
    'city',
    'type'
)

to_graphs_df <- select(only_private_rooms, cols)

View(to_graphs_df)
```

# All this to visualize the data on a map
To visualize the clients' option we will create a map with the score information about each listing to help them out to choose the better option.

```{r install n load the packages to visualize the data}
# install.packages("leaflet")
library(leaflet)
```

```{r create the map}
leaflet(to_graphs_df) %>%
    addTiles() %>%
    addMarkers(
        lng = ~lng, lat = ~lat,
        popup = paste("City: ", to_graphs_df$city, "<br>",
                    "Score: ", to_graphs_df$score, "<br>")
    )
```
