# Process to clean all dataframes

### Dataframe schema

| Column | Description | DType |
| :--- | :--- | :--- |
| `realSum` | the total price of the listing | integer |
| `room_type` | private/shared/entire home/apt | string |
| `room_shared` | indicate if the room is shared | bool |
| `room_private` | indicate if the room is private | bool |
| `person_capacity` | number of people capacity in the room | integer |
| `host_is_superhost` | boolean value indicating if host is a superhost or not | bool |
| `multi` | indicator whether listing is for multiple rooms or not | integer |
| `biz` | business indicator | integer |
| `cleanliness_rating` | rating of the clean level of the room | integer |
| `guest_satisfaction_overall` | overall rating from guests camparing all listings offered by host | integer |
| `bedrooms` | quantity of bedrooms available in the listing | integer |
| `dist` | distance from city center | float |
| `metro_dist` | distance from closest subway station | float |
| `lng & lat` | coordinates for location identification | float |

# Install & load packages
```{r}
install.packages("dplyr")
library(dplyr)
```

```{r}
vienna <- read.csv("/home/igorregly/google-data-analytics-capstone-project/csv_files/vienna_weekends.csv")
```

---
# Cleaning Process
### Checking null data

```{r}
# View(vienna %>% filter(is.na(vienna$metro_dist)))

View(is.na(vienna))

# View(vienna[1633,])
```

### Checking duplicates
